### 2009-11-29 doc/manuals/janitor/tex_usage/usage.tex
Merged usage.tex for the Janitor manual.

The Janitor can be used either with or without the A-REX service.
In case A-REX is used, the invocation of the Janitor will be performed in an automated manner.
It is then triggered by incoming jobs that request a particular RTE for their execution.
If it is not already installed, but available via the Janitor, then it will be installed
without further manual intervention.

@@

In addition to using the Janitor together with A-REX,
the Janitor can also be used as a standalone command line tool.
The available commands are listed in table~\ref{janitor_commandline_man}.
\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands in Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register	& Registers a job and a set of runtime environments in the Janitor database.
				  Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy		& Downloads and installs the desired runtime environments.
				  Requires the name of an already registered [JOB-ID].\\
	&	remove		& Removes the placeholder of the job on the runtime environments.
				  If no more jobs are using the runtime environment and the
				  lifespan of the runtime environment has be expired, the runtime
				  environment can be removed using the \texttt{sweep} command.
				  Requires the [JOB-ID] to be removed.\\
	&			&\\
	&	sweep		& Removes unused runtime environments. No further arguements are required.
				  Using the option \texttt{--force} enforces the removal of all unused
				  runtime environments. Runtime environments having the state FAILED will
				  not be removed.\\
	&	setstate	& Changes the state of a dynamically installed runtime environment.
				  This might be useful in case a runtime environment with a state FAILED
				  shall be removed (new state might be REMOVAL\_PENDING). Requires the argument
				  [STATE] followd by a list of [RTE]s.\\
	&			&\\
	&	search		& Performs a simple search in the catalog and the manually installed
				  runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s,
				  but only a list of string to be searched for.\\
	&	list		& Lists all information about jobs, automatically installed runtime
				  environments and manually installed runtime environments.
				  No additional parameters have to be passed.\\
	&	info		& Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&			& A unique sequence of numbers. Once Janitor registered a job id, it
				  cannot register a second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&			& Runtime environments are defined by a continuous string.
				  The name of valid runtime environment names can be investigated using
				  the \texttt{list} or the \texttt{search} commands. They are defined in
				  the catalog or by the directories and scripts of the \texttt{runtimedir}
				  of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}

The most important commands for the Janitor are \texttt{register},
\texttt{deploy} and \texttt{remove}. To register a job along with a set
of runtime environments in Janitor, the first command \texttt{register}
followed by a job identifier and a list of runtime environments has to be
used.  A job is identified by a sequence of numbers. Runtime environments
are specified by a string containing the name as it is defined within
the Catalog (resp. the runtime directory of the grid-manager).
The command \texttt{deploy} extracts the necessary dependencies of the
desired runtime environments to then download and install the required
packages.

@@

Easy command line examples are provided in Listing~\ref{lst:janitor_example}.

Every command has a certain behaviour for its exit status.
Table~\ref{tab:janitor_commandline_exit_status} lists the possible outcomes.

\begin{table}[!h]
   \begin{center}
        \mycaption{Possible exit states of Janitor}{}
        \label{tab:janitor_commandline_exit_status}
	\begin{tabular}{p{0.5cm}p{2cm}p{0.5cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{Exit status:}} \\
	&\multicolumn{3}{l}{The exit status of Janitor depends on the used command.} \\
	&	register			& 0 & Registration was successful. No noteworthy occurrences.\\
	&					& 1 & Registration was successful but some runtime environments aren't installed yet. Deploy is mandatory.\\ 
	&					& 2 & An error occured.\\
	&					&   &\\
	&	deploy				& 0 & Sucessfully initialized job.\\
	&					& 1 & Can't provide requested runtime environments.\\ 
	&					&   &\\
	&	remove				& 0 & Sucessfully removed job or no such job.\\
	&					& 1 & Can't provide requested runtime environments.\\ 
	&					&   &\\
	&	sweep				& 0 & Always returns this exit code.\\
	&					&   &\\
	&	setstate			& 0 & Changing the state was successful.\\
	&					& 1 & Can not change the state.\\ 
	&					&   &\\
	&	search				& 0 & Search sucessfully finished.\\
	&					&   &\\
	&	list				& 0 & Successfully retrieved information.\\
	&					&   &\\
	&	info				& 0 & Successfully retrieved job information.\\
	&					& 1 & No such job.\\ 
	&					& 2 & Error while retrieving job information.\\
	\end{tabular} 
   \end{center}
\end{table}

>>>>

The Janitor can be used either with or without the A-REX service.
In case
A-REX is used, the invocation of the Janitor will be performed in an
automated manner.  It is then triggered by incoming jobs that request
a particular RTE for their execution.  If it is not already installed,
but
\begin{enumerate}
\item found as a MetaPackage in a Catalog that the site supports
\item with a package that first the BaseSystem of the site
\end{enumerate}
then it will be installed without further manual intervention by the
Janitor - triggered by the A-REX that received the compute request.

The Janitor's installation will not be affected by this decision
pro or cons and integration with \AREX. Both can be installed in
parallel. If \AREX is not allowed to install runtime environments upon
demand, such automated installations can still be invoked manually via
the Janitor's command line  interface.

@@

On Linux systems, the Janitor's standalone commandline tool is
available as /usr/lib/arc/janitor.  Some Linux distributions may
prefer /usr/libexec or similar paths.  The script is only functional as
root\footnote{Should you find that constraint unbearable for your purpose,
please investigate the file rjanitor.cc in the ARC source tree. It wraps
the janitor application and as a C binary can be configured to attract
root privileges.}.  To find that binary directly, you may decide to add
that location to your \$PATH environment variable.

The available commands to the Janitor, implemented as options to the janitor script, are listed
in the Table~\ref{tab:janitor_commandline_man}.

\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands to the Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register & Registers a job and a set of runtime
			   environments in the Janitor database.
			   Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy	 & Downloads and installs the desired
			   runtime environments. Requires the name
			   of an already registered [JOB-ID].\\
	&	remove	 & Removes the placeholder of the job on the runtime environments.
			   If no more jobs are using the runtime environment and the
			   lifespan of the runtime environment has be expired, the runtime
			   environment can be removed using the \texttt{sweep} command.
			   Requires the [JOB-ID] to be removed.\\
	&		 &\\
	&	sweep	 & Removes unused runtime environments. No further arguements are required.
			   Using the option \texttt{--force} enforces the removal of all unused
			   runtime environments. Runtime environments having the state FAILED will
			   not be removed.\\
	&	setstate & Changes the state of a dynamically installed runtime environment.
			   This might be useful in case a runtime environment with a state FAILED
			   shall be removed (new state might be REMOVAL\_PENDING). Requires the argument
			   [STATE] followd by a list of [RTE]s.\\
	&		 &\\
	&	search	 & Performs a simple search in the catalog and the manually installed
			   runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s,
			   but only a list of string to be searched for.\\
	&	list	 & Lists all information about jobs, automatically installed runtime
			   environments and manually installed runtime environments.
			   No additional parameters have to be passed.\\
	&	info	 & Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&		 & A unique sequence of numbers. Once Janitor
			   registered a job id, it cannot register a
			   second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&		& Runtime environments are defined by a continuous
			  string.  The name of valid runtime environment
			  names can be investigated using
			  the \texttt{list} or the \texttt{search}
			  commands. They are defined in the
			  catalog or by the directories and
			  scripts of the \texttt{runtimedir}
			  of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}

The most important commands for the Janitor are \texttt{register},
\texttt{deploy} and \texttt{remove}. To register a job along with a set
of runtime environments in the Janitor, the first command \texttt{register}
followed by a job identifier and a list of runtime environments has to be
used.  A job is identified by a sequence of numbers. Runtime environments
are specified by a string containing the name as it is defined within
the Catalog (resp. the runtime directory of the grid-manager).  The command
\texttt{deploy} extracts the necessary dependencies of the desired
dRTEs and then downloads and installs the required packages.

@@

Easy command line examples are provided in Listing~\ref{lst:janitor_example}.
You may also want to inspect the janitor(8) man page.

Every command has a certain behaviour for its exit status.
Table~\ref{tab:janitor_commandline_exit_status} lists the possible
outcomes. A value of 0 always indicates that no error occurred.

\begin{table}[!h]
   \begin{center}
        \mycaption{Possible exit states of the janitor application}{}
        \label{tab:janitor_commandline_exit_status}
	\begin{tabular}{p{0.5cm}p{2cm}p{0.5cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{Exit status:}} \\
	&\multicolumn{3}{l}{The exit status of Janitor depends on the used command.} \\
	&	register			& 0 & Registration was successful. No noteworthy occurrences.\\
	&					& 1 & Registration was successful but some runtime environments aren't installed yet. Deploy is mandatory.\\ 
	&					& 2 & An error occured.\\
	&					&   &\\
	&	deploy				& 0 & Sucessfully initialized job.\\
	&					& 1 & Can't provide requested runtime environments.\\ 
	&					&   &\\
	&	remove				& 0 & Sucessfully removed job or no such job.\\
	&					& 1 & Can't provide requested runtime environments.\\ 
	&					&   &\\
	&	sweep				& 0 & Always returns this exit code.\\
	&					&   &\\
	&	setstate			& 0 & Changing the state was successful.\\
	&					& 1 & Can not change the state.\\ 
	&					&   &\\
	&	search				& 0 & Search sucessfully finished.\\
	&					&   &\\
	&	list				& 0 & Successfully retrieved information.\\
	&					&   &\\
	&	info				& 0 & Successfully retrieved job information.\\
	&					& 1 & No such job.\\ 
	&					& 2 & Error while retrieving job information.\\
	\end{tabular} 
   \end{center}
\end{table}
